Human Capital Model

### 2015-02-09 paper.tex
Update paper

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=11cm]{p4.pdf}
  \caption{Churn rate-Time Curve}
  \label{churn-rate}
\end{figure}

@@

Still, in each network layer $G_\alpha$, $N_i$ represents emploee
$i$. The edge $e_{ij}$ connects between two nodes $N_i$ and
$N_j$. Each edge has a value $w_{ij}^\alpha$ proving the weight of
edge $e_{ij}^\alpha$, positive correlated to the strength of
connection between two employees in network layers $\alpha$. Then we
connect these network layers together to built a general network
$G_e=(V, E, C)$, V is node set, C is color set, $E\subst V\times
V\times C$ is edge set. In the general model, different layers effects
each other. Take for example, if the friendship between employee $i$
and employee $j$ is deeper, with other conditions the same,their
information flow is more fluent. $w_{ij}^\alpha$ is changing with time
flows and G_e is a dynamic network.

>>>>

Analyzing the consequence of this phenomenon, we use our program to
simulate this process. As a result, we find a organizational churn in
our simulation as shown in Figure \ref{organizational-churn}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=4cm]{Pic3_0.png}
  \includegraphics[width=4cm]{Pic3_1.png}
  \includegraphics[width=4cm]{Pic3_2.png}
  \includegraphics[width=4cm]{Pic3_3.png}
  \includegraphics[width=4cm]{Pic3_4.png}
  \caption{Organizational Churn}\label{organizational-churn}
\end{figure}

The black spots in the graph denote employees who have churned

@@

\begin{figure}[htb]
  \centering
 % \includegraphics[width=11cm]{p4.pdf}
  \caption{Churn rate-Time Curve}
  \label{churn-rate}
\end{figure}

@@

Still, in each network layer $G_\alpha$, $N_i$ represents emploee
$i$. The edge $e_{ij}$ connects between two nodes $N_i$ and
$N_j$. Each edge has a value $w_{ij}^\alpha$ proving the weight of
edge $e_{ij}^\alpha$, positive correlated to the strength of
connection between two employees in network layers $\alpha$. Then we
connect these network layers together to built a general network
$G_e=(V, E, C)$, V is node set, C is color set, $E \subset  V\times
V\times C$ is edge set. In the general model, different layers effects
each other. Take for example, if the friendship between employee $i$
and employee $j$ is deeper, with other conditions the same,their
information flow is more fluent. $w_{ij}^\alpha$ is changing with time
flows and $G_e$ is a dynamic network.
